Healthcare Insights and Sociodemographic Analysis of New York: A Comprehensive Analysis of Patient Records in 2013

### 2023-09-23 STAT405Project.qmd
horizontal boxplot

boxplot(cleaned_data$'Total Costs', 
        main="Box Plot of Total Costs (Outliers Truncated)",
        ylab="Total Costs")
```
### Plot Desciption and Inferencing

@@

## **Plot 4: Trends in Total Charges and Length of Stay**
```{r}
#| echo: false

>>>>

boxplot(cleaned_data$'Total Costs', 
        main="Box Plot of Total Costs (Outliers Truncated)",
        ylab="Total Costs",
        horizontal = TRUE)
```
### Plot Desciption and Inferencing 
The following boxplot refers to our Total Cost data and is representative of our data that has been cleaned to remove outliers that are in our top 5% of data points, meaning that the outliers that are extremely high are cleaned out.

@@

## **Plot 4: Trends in Total Charges and Length of Stay**
```{r warning = FALSE}
#| echo: false
